### 2018-03-13 paper/5-implementations.tex
Rename trackDependencies to track

\begin{minted}{haskell}
recursive
    :: (m ~ M i k v, Default i)
    => (k -> Maybe [k] -> (k -> m v) -> m ([k], v) -> m ())
    -> Build Monad i k v
recursive step compute = runM . ensure
    where
        ensure k = do
            let fetch x = ensure x >> getStore x
            done <- getTemp
            when (k `Set.notMember` done) $ do
                modifyTemp $ Set.insert k set
                case trackDependencies compute fetch k of
                    Nothing -> return ()
                    Just act -> step k (getDependenciesMaybe compute k) fetch act
\end{minted}

>>>>

\begin{minted}{haskell}
recursive
    :: (m ~ M i k v, Default i)
    => (k -> Maybe [k] -> (k -> m v) -> m ([k], v) -> m ())
    -> Build Monad i k v
recursive step compute = runM . ensure
    where
        ensure k = do
            let fetch x = ensure x >> getStore x
            done <- getTemp
            when (k `Set.notMember` done) $ do
                modifyTemp $ Set.insert k set
                case track compute fetch k of
                    Nothing -> return ()
                    Just act -> step k (getDependenciesMaybe compute k) fetch act
\end{minted}
